---
title: "Hod_2023-05-04"
author: "Martin Kopecký"
date: "2023-05-04"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
rm(list=ls()) # smaz vsechny promenne
print(ls())
library(ggplot2)
library(dplyr)
library(tidyr)
```
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Test slide ??

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r}
  scatter.smooth(iris$Sepal.Length, iris$Sepal.Length, xlab="x", ylab="y")
```

## Graph 2
```{r}
names <- c("Petal" , "Sepal")
valls <- c(mean(iris$Petal.Length),mean(iris$Sepal.Length))

mydata <- data.frame(names, valls)

mplot <- ggplot(mydata, aes(x=names,y=valls,fill=names)) + geom_bar(stat="identity") 
mplot + scale_y_continuous(breaks = seq(0,6,0.25)) + coord_fixed(ratio = 1/1.5)

```

## Graph 3
```{r message=FALSE, warning=FALSE}
names <- c("Petal" , "Sepal")
valls <- c(mean(iris$Petal.Length),mean(iris$Sepal.Length))

mydata <- data.frame(names, valls)

mplot <- ggplot(mydata, aes(x=names,y=valls,fill=names)) + geom_bar(stat="identity") 
mplot + scale_y_continuous(breaks = seq(0,6,0.25)) + coord_fixed(ratio = 1/1.5) + coord_polar("y")

```

## Graph 4
```{r}
iris %>% ggplot(aes(x=Species,y=Petal.Length)) + geom_boxplot()
```

